%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{color}
\usepackage{hyperref}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear alLifang Header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Chenhang Cui} \\ \vspace{1pt}
    \small (+86)15209187803 $|$ \href{mailto:chenhangcui@gmail.com}{\underline{chenhangcui@gmail.com}} $|$
    \href{https://scholar.google.com/citations?user=V5X1gdAAAAAJ}{\underline{Google scholar}} $|$
    \href{https://github.com/chenhangcuisg-code}{\underline{GitHub page}}
    $|$
    \href{https://chenhangcuisg-code.github.io/}{\underline{Chenhang's homepage}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {National University of Singapore, School of Computing (NExT++ Lab)} {Singapore}
      {Ph.D. in Computer Science, Advisor: Prof. Chua Tat-Seng; with Dr. Fei Shen}{Jan. 2026 - Present}
    \resumeSubheading
      {University of Electronic Science and Technology of China} {Chengdu, China}
      {Bachelor of Yingcai Honors College}{Sept. 2021 - Jun. 2025}
   \resumeSubheading
      {The Middle School Attached To Northwestern Polytechnical University} {Xi'an, China}
      {High School Diploma}{Sept. 2018 - Jun. 2021}
          \resumeItemListStart
            \resumeItem{GPA: 3.98/4.00\quad Average Score: 90.51  \quad Rank: 2/70 \quad TOEFL: 97}
        \resumeItem{About me: I am very interested in large models and aspire to become an artificial intelligence scientist in the future. I enjoy making friends and in my daily life, I love running and traveling.}
         \resumeItem{Research interests: Large Vision-language Models (LVLMs): Trustworthiness in large vision-language models, (hallucination, attack, etc.), Alignment of LVLMs, RL in LVLMs;
            Multi-view Representation Learning: Exploring better representations for multimodal data in the real world}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Conference paper (*Equal contribution)}}{}
      \resumeItemListStart

        \resumeItem{1. \textbf{Chenhang Cui}, Gelei Deng, An Zhang, Jingnan Zheng, Yicong Li,
        Lianli Gao, Tianwei Zhang, Tat-Seng Chua.
        \textit{Safe + Safe = Unsafe? Exploring How Safe Images Can Be Exploited to Jailbreak
        Large Vision-Language Models.}
        NeurIPS, 2025.
        \href{https://arxiv.org/pdf/2411.11496}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{2. \textbf{Chenhang Cui}, An Zhang, Yiyang Zhou, Zhaorun Chen, Gelei Deng, Huaxiu Yao, Tat-Seng Chua.
        \textit{Fine-Grained Verifiers: Preference Modeling as Next-Token Prediction in Vision-Language Alignment.}
        ICLR, 2025.
        \href{https://arxiv.org/pdf/2410.14148.pdf}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{3. Peng Xia, Siwei Han, Shi Qiu, Yiyang Zhou, Zhaoyang Wang, Wenhao Zheng, Zhaorun Chen, \textbf{Chenhang Cui}, Mingyu Ding, Linjie Li, Lijuan Wang, Huaxiu Yao.
        \textit{Mmie: Massive multimodal interleaved comprehension benchmark for large vision-language models.}
        ICLR, 2025.
        \href{https://arxiv.org/pdf/2410.10139}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{4. Haoqin Tu*, \textbf{Chenhang Cui}*, Zijun Wang, Yiyang Zhou, Bingchen Zhao, Junlin Han, Wangchunshu Zhou, Huaxiu Yao, Cihang Xie.
        \textit{How Many Unicorns Are in This Image? A Safety Evaluation Benchmark for Vision LLMs.}
        ECCV, 2024.
        \href{https://arxiv.org/pdf/2311.16101.pdf}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{5. Yiyang Zhou*, \textbf{Chenhang Cui}*, Jaehong Yoon, Linjun Zhang, Zhun Deng, Chelsea Finn, Mohit Bansal, Huaxiu Yao.
        \textit{Analyzing and Mitigating Object Hallucination in Large Vision-Language Models.}
        ICLR, 2024.
        \href{https://arxiv.org/pdf/2310.00754.pdf}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{6. Yiyang Zhou*, \textbf{Chenhang Cui}*, Rafael Rafailov, Chelsea Finn, Huaxiu Yao.
        \textit{Aligning Modalities in Vision Large Language Models via Preference Fine-tuning.}
        ICLR Workshop, 2024.
        \href{https://arxiv.org/pdf/2402.11411}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{7. Zhaorun Chen, Yichao Du, Zichen Wen, Yiyang Zhou, \textbf{Chenhang Cui}, Zhenzhen Weng, Haoqin Tu, Chaoqi Wang, Zhengwei Tong, Qinglan Huang, Canyu Chen, Qinghao Ye, Zhihong Zhu, Yuqing Zhang, Jiawei Zhou, Zhuokai Zhao, Rafael Rafailov, Chelsea Finn, Huaxiu Yao.
        \textit{MJ-Bench: Is Your Multimodal Reward Model Really a Good Judge?}
        ICML Workshop, 2024.
        \href{https://openreview.net/pdf?id=H6eELDnYvd}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{8. \textbf{Chenhang Cui}, Yazhou Ren, Jingyu Pu, Jiawei Li, Xiaorong Pu, Tianyi Wu, Yutao Shi, Lifang He.
        \textit{A Novel Approach for Effective Multi-View Clustering with Information-Theoretic Perspective.}
        NeurIPS, 2023.
        \href{https://arxiv.org/pdf/2309.13989.pdf}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{9. \textbf{Chenhang Cui}, Yazhou Ren, Jingyu Pu, Xiaorong Pu, Lifang He.
        \textit{Deep Multi-view Subspace Clustering with Anchor Graph.}
        IJCAI, 2023.
        \href{https://www.ijcai.org/proceedings/2023/0398.pdf}{\textcolor{cyan}{[pdf]}}}

        \resumeItem{10. Jingyu Pu, \textbf{Chenhang Cui}, Xinyue Chen, Yazhou Ren, Xiaorong Pu, Zhifeng Hao, S Yu Philip, Lifang He.
        \textit{Adaptive Feature Imputation with Latent Graph for Deep Incomplete Multi-View Clustering.}
        AAAI, 2023.
        \href{https://ojs.aaai.org/index.php/AAAI/article/download/29380/30606}{\textcolor{cyan}{[pdf]}}}

      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Arxiv}}{}
      \resumeItemListStart
        \resumeItem{1. \textbf{Chenhang Cui}*, Yiyang Zhou*, Xiangyu Yang, Shirley Wu, Linjun Zhang, James Zou, Huaxiu Yao. Holistic Analysis of Hallucination in Large Vision-Language Models: Bias and Interference Challenges
        \href{https://arxiv.org/pdf/2311.03287.pdf}{\textcolor{cyan}{[pdf]}}}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {PhD: Trustworthy and Aligned Vision-Language Models}{Jan. 2026 -- Present}
  {Advisor: Prof. Chua Tat-Seng; working with Dr. Fei Shen (NUS, NExT++ Lab)}{}
  \resumeItemListStart
    \resumeItem{\textbf{Topic}: Hallucination, safety, and RL-based alignment for large vision-language models.}
  \resumeItemListEnd

\resumeSubheading
  {Research Intern: Safety and Multimodal RL Alignment for VLLMs}{Aug. 2024 -- Aug. 2025}
  {Host: Prof. An Zhang (NUS, NExT++ Lab)}{}
  \resumeItemListStart
    \resumeItem{\textbf{Topic}: Safety and Multimodal RL Alignment for VLLMs}
    \resumeItem{\textbf{Description}: Focused on enhancing the safety and alignment of Vision-Language Large Models (VLLMs) by addressing issues of unsafe and misaligned multimodal content generation. The project involves evaluating existing VLLMs, developing new alignment techniques, and assessing their safety.}
    \resumeItem{\textbf{Achievements}: One paper has been accepted by ICLR, 2025. One paper has been accepted by NeurIPS, 2025.}
  \resumeItemListEnd

    \resumeSubheading
      {Research Intern: Reducing Hallucination in Large Vision-Language Models}{May 2023 -- Jan. 2024}
      {Host: Prof. Huaxiu Yao (UNC MURGe-Lab)}{}
      \resumeItemListStart
        \resumeItem{\textbf{Topic}: Reducing object hallucination problems in Large Vision-Language models}
        \resumeItem{\textbf{Description}: Aiming to reduce hallucination in existing Large Vision-Language models (e.g., LLaVa, MiniGPT-4, mPlug-owl).}
        \resumeItem{\textbf{Achievements}: Reduced hallucination by 23\% without compromising text diversity in MiniGPT-4. Human and GPT assessments rank our methods as number one. Short version accepted by NeurIPS Workshop, 2023; long version accepted by ICLR. (Conference - 1)}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research: Representation Learning from Multi-view Perspective}{May 2022 -- Sep. 2023}
      {Advisor: Prof. Yazhou Ren (UESTC)}{}
      \resumeItemListStart
        \resumeItem{\textbf{Topic}: Consistency and Complementary of Multimodal Representations}
        \resumeItem{\textbf{Description}: Enhancing representation learning through consistency from multimodal data, applied to downstream ML tasks.}
        \resumeItem{\textbf{Achievements}: Three papers completed (Conference - 2, 4, 5)}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SERVICES-----------
\section{Services}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Conference Reviewer}} {}

          \resumeItemListStart
            \resumeItem{ARR 2024, KDD 2024, ICLR 2025, CVPR 2025, ICLR 2026}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Journal Reviewer}} {}

          \resumeItemListStart
            \resumeItem{Neural Networks}
          \resumeItemListEnd
             \resumeSubHeadingListEnd

%-----------HONORS-----------
\section{Honors \& Awards}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{UESTC Undergraduate Academic Scholarship}}{2022, 2023, 2024}
      \resumeProjectHeading
          {\textbf{HUAWEI Scholarship}}{2023}
      \resumeProjectHeading
          {\textbf{The Mathematical Contest in Modeling}:  Honorable Mention (15\%), Student Advisor}{2024}
           \resumeProjectHeading
    {\textbf{SenseTime Scholarship}: \normalsize This award is presented to undergraduate students with  outstanding \\  \normalsize contributions
    in the field of computer science.  Only 25 students received this award in 2024.}{2024}

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, Latex, Git, Matlab, Shell, MarkDown, Html} \\
     \textbf{Communication}{: Chinese (native), English (TOEFL: 97 - Reading: 24, Listening: 27, Speaking: 21, Writing: 25)}
    }}
\end{itemize}


%-------------------------------------------
\end{document}
